\section{Goal}		% rename this
\label{sec:goal}

\subsection{Idea}

This project will continue my research from this summer as part of a Research Experiences for Undergraduates (REU) at Montana State University.
My collaborators and I came up with the following idea.

Like Matzutt and his collaborators, we allow recent miners to vote \cite{matzutt2020HowTSPrune}.
However, we choose to store votes in a distributed hash table.
Storing votes in a distributed hash table is convenient because it allows recent miners to vote immediately, but it also gives attackers an opportunity to delete votes.
To combat vote deletion, we drew on the idea of a tangle \cite{popov2016Tangle}.
A tangle is a directed acyclic graph where the nodes are added to tangle by selecting the two most recently added nodes as parents.
In this context, nodes are realized as votes.
A tangle manager receives votes from recent miners and adds each of them to the tangle by attaching them to parent votes.

\input{tikz/tangle}

A vote is invalid if one if its parents is invalid or deleted.
Deleting a vote causes a chain reaction in the tangle that deletes votes that support the attacker, preventing the attacker from swinging the election, by disproportionately deleting votes on one side of the election.
A bootstrapping node can request the vote tangle and then make a decision based on valid votes.

While we do have a sketch of a solution idea, more work needs to be done to prove its correctness and security as well as to demonstrate these properties through a practical implementation.
Preliminary results indicate that it is resistant to some types of attacks but we need to consider smarter and more powerful attackers.

\subsection{Implementation}

