\section{Methodology}
\label{sec:methodology}

% provide enough information so that someone can replicate

Much of this project is devising a method to bootstrap blockchain nodes.
Since this is a conceptual task, it cannot be replicated.
However, the experimental verification of our protocol can be replicated.
Section \ref{sec:methodology} is devoted to providing the necessary information for someone to replicate our implementation.

% network simulator with dht

In order to match our model as closely as possible with our implementation, we chose to implement our solution on a network simulator using a full-fledged DHT.
This is not strictly necessary but we felt that it made our results more applicable to a real implementation of our idea.

% digitally signed parents

A neglected detail of the solution is the process of selecting parents in the tangle.
The tangle manager has complete control over \textit{which} votes are selected as parents, but we require that the parents are digitally signed in the vote.
This means that the manager must tell the voter which votes are the parents and the voter includes that information in their vote.
While this introduces some overhead communication for our solution, it prevents a malicious actor from changing the structure of a tangle to their advantage.

% attacker intelligence

The most important aspect of the implementation is the intelligence of the attackers.
We expect the constraints of our solution to prevent an attacker from \textit{successfully} fooling a bootstrapping node.
But the only way we can verify this is to simulate intelligent attackers.
We have divided attacks into two categories: deleting votes and rejecting votes.
An accurate replication of this project should at least implement these strategies.
Implementing more strategies is welcome, since it provides more information on our system!

\subsection{Design}

The design pattern that appears in this project is the Strategy Pattern.
The design pattern presents itself in the sorting styles used to generate the charts in Section \ref{sec:results}.
We have no canonical ordering for the votes in a tangle so we implemented a number of them and chose between them.
To make the code cleaner, we use the Strategy Pattern.
We have an IVoteSorter interface with a method called \textit{sortedVotes()} that returns a sorted array of vote keys.
Each class implements a different partial ordering that allows us to to sort the votes.
The class RndSorter implements sorting by the vote's round.
BFSSorter returns the order votes are encountered in a breath first search.
Finally, DescSorter returns the votes in the order of the number of descendants each vote has.
For the final charts, we decided to use the RndSorter class but the design pattern helped keep our code clean and organized.
Figure \ref{fig:strategy} shows a visual of our Unified Modeling Language diagram for this pattern.

\input{tikz/uml}
